---
title: "Untitled"
author: "Peter Kolodziej pgk2115"
date: "4/30/2019"
output: flexdashboard::flex_dashboard
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(rmarkdown)
library(knitr)
library(Hmisc)
library(DT)
library(syuzhet)
library(data.table)
library(reticulate)
library(glue)
library(keras)
import("pickle")
import("keras")
import("numpy")

assignInNamespace("cedta.override", c(data.table:::cedta.override,"rmarkdown"), "data.table")


opts_chunk$set(echo = FALSE, comment="", warning = FALSE, message = FALSE, tidy.opts=list(width.cutoff=55), tidy = TRUE)
review<-fread("/Users/11kolop/Downloads/review_restaurants")

```



Sentiment Analysis
=====================================  

Row {data-height=500}
-------------------------------------

```{r}
inputPanel(
  selectInput(inputId="SS", label = " Star Level", choices = c(1:5), selected = c(1:5)[1]))


renderPlot({
d<-get_nrc_sentiment(review[review$stars==input$SS,]$text)
td<-data.frame(t(d))
td_new <- data.frame(rowSums(td))
names(td_new)[1] <- "count"
td_new <- cbind("sentiment" = rownames(td_new), td_new)
rownames(td_new) <- NULL
qplot(sentiment, data=td_new[1:8,], weight=count, geom="bar",fill=sentiment)+ggtitle("Sentiments")
})
```

Review Prediction
===================================


Row {data-height=500}
-------------------------------------

```{r}
textAreaInput("text", label = h3("Place Review Here"), width = '600px', height = '300px')
actionButton("submit", "Submit")
v <- reactiveValues()
renderUI(v[["py_chunk"]])
observeEvent(
  input$submit,
  {
    var <- input$text
py_code <- c(
       "```{python, echo=F}",
      "import pickle",
      "from keras.models import load_model",
      "from keras.preprocessing.sequence import pad_sequences",
      "from keras.preprocessing.text import Tokenizer",
      "import numpy as np",
      "revi = str(r.var)",
      "model = load_model('my_model.h5')",
      "with open('tokenizer.pickle', 'rb') as handle:
      tokenizer = pickle.load(handle)",
      "revi = np.expand_dims(revi, axis=0)",
      "revi = tokenizer.texts_to_sequences(revi)",
      "revi = pad_sequences(revi,maxlen=200)",
      "revi = model.predict([revi], batch_size=1, verbose = 0).argmax()+1",
      "print(revi,'stars')",
      "```"
    )
    v[["py_chunk"]] <-HTML(knit(text = py_code))})
```
